\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-28 paper/intersection.tex
Fix graph in Sec. 3

\begin{figure}
\centering
\includegraphics[width=0.99\columnwidth]{intersectionchart.pdf}
\caption{Comparison of Lawful Intersection Performance}
\label{fig:isectgraph}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{tikzpicture}
\begin{loglogaxis}[
	title={Parallel vs. Sequential Running Time},
	xlabel={Total Set Size [Ciphertexts]},
	ylabel={Running Time [min]},
	xmin=10, xmax=200000,
	ymin=0.01, ymax=1000,
	%xtick={10, 100, 1000, 10000, 100000},
	%ytick={0.01, 0.1, 1, 10, 100, 1000},
	log ticks with fixed point,
	legend pos=north west,
	ymajorgrids=true,
	xmajorgrids=true,
	grid style=dashed,
]

\addplot[
	color=blue,
	mark=o,
	]
	table [x=Items, y=Parallel, col sep=comma] {intersection.csv};

\addplot[
	color=red,
	mark=square,
	]
	table [x=Items, y=Sequential, col sep=comma] {intersection.csv};

\legend{Parallel, Sequential}
\end{loglogaxis}
\end{tikzpicture}
\captionsetup{justification=centering}
\caption{Comparison of Lawful Intersection Performance}
\label{fig:isectgraph}
\end{figure}
